Analysis of the 2005--\myrevision{2016} Earthquake Sequence in Northern Iran Using the Visibility Graph Method

### 2017-06-21 results.tex
update to paag revision

@@

We now investigate the relationship of the parameters obtained through the visibility graph analysis with time. Here, the visibility graph analysis is done by windows of equal number of events moving in time across the catalog sequence. The number of events in the window is kept fixed independently of the time between them, and the results are associated with the last event in the window. In this case, we are interested in using a small number of events to capture the relevance of each new event as the window moves in time. We tried different \myrevision{window size (20-100 events per window) for each seismic zone. The characteristics of major events are not considerably changing due to window size. There is a trade of in choosing the window size. Small windowing size will highlight the local changes in the time series, however, in the mean time it won't represent a true seismicity characteristic of the subsample (e.g., b-value). We choose window size as 50 to be small enough to represent the variation of k-M, b-value and Tc in time and large enough in agreement with Woessner and Wiemer (2005) who found that at least the number of events has to be 50 to get reliable estimate of b-value.} At this point it is also of interest to compute the value of <$T_c$> explained in the Methodology section.

Figure \ref{fig:tc} shows the variation of <$T_c$>, the $k$-$M$ slope, and the $b$-value with time for each of the three seismic zones in northern Iran. The time-magnitude sequence is also included for reference. Note that the behavior of the $k$-$M$ slope and the $b$-value is very similar along time for all three zones. \myrevision{Specially in the case of Alborz where because of higher number of events the correlation is easily seen.} This is consistent with the results presented before. We note that there seems to be a correlation between the behavior of the $b$-value in time with the occurrence of some of these larger events. In particular, some of the events in the figure seem to coincide with a drop in the $b$-value.

>>>>

We now investigate the relationship of the parameters obtained through the visibility graph analysis with time. Here, the visibility graph analysis is done by windows of equal number of events moving in time along the catalog sequence. The number of events in the window is kept fixed independently of the time between them, and the results are associated with the last event in the window. In this case, we are interested in using a small number of events to capture the relevance of each new event as the window moves in time. We tried different \myrevision{window sizes between 20 and 100 events per window for each seismic zone. As it is natural to expect, there are trade-offs between different window-sizes. Smaller window sizes emphasize the local changes in the time series, but are less reliable when it comes to the seismicity parameters (e.g., $b$ value). Larger window sizes, on the other hand, offer less insight into the time dependence of the window sequence characteristics. We chose a window size $n = 50$, which is consistent with the suggested minimum number of events acceptable to estimate $b$ according to \citet{Woessner_2005_BSSA}.}

\myrevision{In this windowing analysis, in addition to $b$ and the $k$-$M$ slope, we are interested in computing} the value of $<$$T_c$$>$ explained in the Methodology section. Figure \ref{fig:tc} shows the variation of the $k$-$M$ slope, the $b$-value, and $<$$T_c$$>$ with time for...

@@

each of the three seismic zones in northern Iran. The time-magnitude sequence is also included for reference. Note that the behavior of the $k$-$M$ slope and the $b$-value is very similar along time for all three zones. \myrevision{Specially in the case of Alborz where because of higher number of events the correlation is easily seen.} This is consistent with the results presented before. We note that there seems to be a correlation between the behavior of the $b$-value in time with the occurrence of some of these larger events. In particular, some of the events in the figure seem to coincide with a drop in the $b$-value.

### 2017-06-21 seismicity.tex
update to paag revision

\begin{figure*}[t]
	\centering
	a)
	\includegraphics[width=\textwidth]{figures/pdf/figure-03} \\
	b)
	\includegraphics[width=\textwidth]{figures/pdf/figure-03} 
	\caption{\myrevision{Instrumental} seismicity of northern Iran for the 2005--\myrevision{2016} period, considering only the events in the seismic zones of interest, namely Azerbaila, Alborz, and Kopeh Dagh. The size of symbols are proportional to the magnitude of the events, as indicated by the artificial scale shown on the right. The background shows fault lines and the shaded relief. The color version of this figure is available only in the electronic edition.}
	\label{fig:seismicity}
\end{figure*}

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-04-rev} 
	\caption{\myrevision{Completeness magnitude vs time results and selected $M_c$ values for the three tectonic seismic regions in northern Iran as evaluated from the time-magnitude sequence of earthquakes during the 2005--2016 period.}}
	\label{fig:completeness}
\end{figure*}

>>>>

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-03} 
	\caption{\myrevision{Instrumental seismicity of northern Iran for the 2005--2016 period, considering only the events in the seismic zones of interest, namely Azerbaila, Alborz, and Kopeh Dagh, for the whole (a) and complete (b) catalogs.} The size of symbols are proportional to the magnitude of the events, as indicated by the artificial scale shown on the right. The background shows fault lines and the shaded relief. The color version of this figure is available only in the electronic edition.}
	\label{fig:seismicity}
\end{figure*}

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-04} 
	\caption{\myrevision{Completeness magnitude, $M_c$, as a function of time (in years) for the three seismic zones in the region of interest, corresponding to the time-magnitude sequences of earthquakes during the 2005--2016 period.}}
	\label{fig:completeness}
\end{figure*}
